Partial Identifiability

### 2016-07-18 identify/adjust/adjust.tex
starts trying to define the adjustment problem

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{times}
\usepackage{fullpage}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{accents}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{dsfont}
\usepackage[bf]{caption}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\usepackage{amsthm}
\usepackage{natbib}
\usepackage[capitalize]{cleveref}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{tikz} 
\usetikzlibrary{arrows,positioning} 
\pgfarrowsdeclarecombine{ring}{ring}{}{}{o}{o}
%\DeclareMathOperator{\ringarrow}{\raisebox{0.5ex}{\tikz[baseline]{\draw[ring->](0,0)--(2em,0);}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MACROS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\defined}{\vcentcolon =}
\newcommand{\rdefined}{=\vcentcolon}
\newcommand{\E}{\mathbb E}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\calF}{\mathcal F}
\newcommand{\sr}[1]{\stackrel{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\ind}[1]{\mathds{1}\!\!\set{#1}}
\newcommand{\argmax}{\operatornamewithlimits{arg\,max}}
\newcommand{\argmin}{\operatornamewithlimits{arg\,min}}
\newcommand{\floor}[1]{\left \lfloor {#1} \right\rfloor}
\newcommand{\ceil}[1]{\left \lceil {#1} \right\rceil}
\newcommand{\eqn}[1]{\begin{align}#1\end{align}}
\newcommand{\eq}[1]{\begin{align*}#1\end{align*}}
\newcommand{\Ber}{\operatorname{Bernoulli}}
\renewcommand{\P}[1]{\operatorname{P}\left\{#1\right\}}

\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    observed/.style={
           circle,
           rounded corners,
           draw=black, thick,
           minimum width=1em,
           minimum height=1em,
           font=\footnotesize,
           text centered,
           fill=blue!20!white},
     latent/.style={
           circle,
           rounded corners,
           draw=black, thick, dashed,
           minimum width=.5em,
           minimum height=.5em,
           font=\footnotesize,
           text centered,
           fill=black!10!white
           },
    % Define arrow style
    pil/.style={
           o->,
           thick,
           shorten <=2pt,
           shorten >=2pt,},
    sh/.style={ shade, shading=axis, left color=red, right color=green,
    shading angle=45 }  
}

@@

\title{Intervention Bandits}
\author{Blah blah}

\begin{document}
\def\ci{\perp\!\!\!\perp}
\maketitle

\begin{abstract}
An abstract.
\end{abstract}

\section{Introduction}

Useful references are: \cite{BC12}.

\section{Notation}

Assume we have a known causal model with binary variables $\boldsymbol{X} = \{X_{1}..X_{K}\}$ that independently cause a target variable of interest $Y$, figure . We can run sequential experiments on the system, where at each timestep $t$ we can select a variable on which to intervene and subsequently observe the complete result, $(\boldsymbol{X}_{t},Y_{t})$ This problem can be viewed as a variant of the multi-armed bandit problem.

Let $p \in [0,1]^K$ be a fixed and known vector. In each time-step $t$:

\begin{enumerate}
\item The learner chooses an $I_t \in \set{1,\ldots, K}$ and $J_t \in \set{0,1}$.
\item Then $X_t \in \set{0,1}^K$ is sampled from a product of Bernoulli distributions, $X_{t,i} \sim \Ber(p_i)$ 
\item The learner observes $\tilde X_t \in \set{0,1}^K$, which is defined by 
\eq{
\tilde X_{t,i} = \begin{cases}
X_{t,i} &\text{if } i \neq I_t \\
J_t & \text{otherwise}\,.
\end{cases}
}
\item The learner receives reward $Y_t \sim \Ber(q(\tilde X))$ where $q:\set{0,1}^K \to [0,1]$ is unknown and arbitrary.
\end{enumerate}
The expected reward of taking action $i,j$ is $\mu_{i,j} = \E[q(X)|do(X_i = j)]$. The optimal reward and action are $\mu^*$ and $(i^*,j^*)$ respectively,
where $(i^*,j^*) = \argmax_{i,j} \mu_{i,j}$ and $\mu^* = \mu(i^*,j^*)$. The $n$-step cumulative expected regret is
\eq{
R_n = \E \sum_{t=1}^n \left(\mu^* - \mu_{I_t,J_t}\right).
}
\pagebreak

\section{Estimating $\mu_{i,j}$}
The most natural way to estimate $\mu_{i,j}$ is to compute an empirical estimate based on samples when that action was taken. This approach would
lead directly to the UCB algorithm with $2K$ actions and a regret bound that depended linearly on $K$.

In this instance we can significantly
outperform the standard approach by exploiting the known causal structure of the problem.

\eqn {
P(Y|do(X_i=j)) &= P(Y|X_i = j)\\
 &= \sum_{b}P(Y|X_i = j,X_a = b)P(X_a = b|X_i = j) \\
 &= \sum_{b}P(Y|X_i = j,X_a = b)P(X_a = b), \; \forall \, a \in \{1...K\}/i \text{ as } X_a \ci X_i\\
 \label{eqn:marginalizedEstimator}
 &= \sum_{b}P(Y|X_i = j,do(X_a = b))P(X_a = b) 
}

\subsection{Estimators}
\label{sec:estimators}
Fix some time-step $t$ and $i \in \set{1,\ldots,K}$ and $j \in \set{0,1}$.

Considering equation \ref{eqn:marginalizedEstimator}, a natural way to construct an empirical estimator,  $\hat{\mu}_a$, for $P(Y|do(X_i=j))$ utilizing the information obtained by intervening on variable $a$ is:

\eqn {
\hat{\mu}_a &=
\begin{cases}
\label{eqn:marginalizedEstimator2}
\frac{m_{a,1}}{n_{a,1}}p_a+\frac{m_{a,0}}{n_{a,0}}(1-p_a) & \text{if } a \neq{i} \\
\frac{m_{i,j}}{n_{i,j}} & \text{if } a=i \\
\end{cases}\\
}
where $\frac{m_{a,b}}{n_{a,b}}$ is an empirical estimator for $P(Y|X_i = j,do(X_a = b))$,
\eqn{
m_{a,b}   &= \sum_{s=1}^t \ind{X_i = j, I = a,J = b, Y = 1}_s \\
n_{a,b}    &= \sum_{s=1}^t \ind{X_i = j, I = a,J = b}_s 
}

This gives $K$ estimators $\{\hat{\mu_1}...\hat{\mu_K}\}$ to be pooled into a single estimator $\hat{\mu}$.

\eqn {
\label{eqn:pooledEstimators}
\hat{\mu} &= \sum^{K}_{a=1}w_a\hat{\mu}_a=w_i \frac{m_{i,j}}{n_{i,j}}+ \sum_{a \neq i} w_a \left[p_a \frac{m_{a,1}}{n_{a,1}} + (1 - p_a) \frac{m_{a,0}}{n_{a,0}}\right]\\
}

If $p$ is not known $p_a$ could be replaced with its empirical estimate $\hat{p}_a$

\eqn{
\hat{p}_a = \frac{\sum_{s=1}^{t} \ind{X_a=1,I \neq a}_s}{\sum_{s=1}^{t} \ind{I \neq a}_s}
}

Now I want to select weights $w$ to minimize the variance in $\hat{\mu}$ and then get some kind of high probability bound for it. However, if I'm not very careful about how I pool things in equation \ref{eqn:pooledEstimators}, the estimator could get very biased, ie estimators $\hat{\mu_a}$ where I have data only for one state of the variable $a$ are not very informative, so should tend to get low weight, but if we choose to sample the second state based on previous payoffs - then we could end up assigning high weights to those estimators that had fluctuated above the true value...

This complicates getting correct uncertainty bounds for a UCB type algorithm/proof.

Consider, what exactly you mean by not unbiased ...

\section{Importance Sampling Approach}

Consider down weighting estimators proportional to the number of times we played them

\section{Observe then exploit}

\subsection{Basic idea}

Basic idea - observe until the uncertainty on all actions is smaller than $\epsilon$, then exploit (or switch to standard UCB). This is only really going to work if $p_a \sim 0.5$.

Bounds on regret: when observing the regret for each timestep is at most 1 (since the reward is $\in [0,1]$). When exploiting regret it at most $\epsilon$. If the horizon is $n$, the cost of exploiting $< \epsilon n$ and the cost of observing is $O(1/\epsilon^2)$ (this comes from how quickly we converge to within $\epsilon$ for all arms).

\eqn{
R_n = O(n\epsilon+\frac{1}{\epsilon^2})
}

Differentiating and selecting $\epsilon = (\frac{2}{n})^{1/3}$ to minimize the regret yields:

\eqn{
R_n = O(n^{2/3})
}

For each arm $X_i = j$, we have:

\eqn{
\hat{\mu}_{ij} = \frac{m_{ij}}{n_{ij}}
}

where

\eqn{
m_{i,j}    &= \sum_{s=1}^t \ind{X_i = j, Y = 1} \\
n_{i,j}    &= \sum_{s=1}^t \ind{X_i = j} \\
}

and Hoeffding's Inequality gives:

\eqn {
P\left(|\hat{\mu}_{ij} - \mu_{ij}| > \sqrt{\frac{1}{2n_{ij}}\log{\frac{2}{\delta}}}\right) \leq \delta
}

\subsection{Alternate Observe and Exploit With Some Decay}
Keep track of two separate bounds and always choose the narrower of the two.

\subsection{Observe until number of plausibly optional arms $< \alpha$}

Define the set of plausibly optimal arms to be those with an upper confidence bound that is higher than the largest lower confidence bound.

\eqn {
A_t = \{k : UB(k) \geq max_{k'}(LB(k'))  \}
}

We then observe until the size of this set is less than some value $\alpha$ before switching to UCB. This takes into account that we don't need narrow confidence bounds on the arms with very low expected reward. Once we start doing UCB, we keep track of the ucb bound separately and for each arm use whichever bounds are narrower.

\subsubsection{Regret during observe phase}

Let $n$ be the number of timesteps until the size of the set $A_t$ falls below $\alpha$ or we reach the overall horizon $T$

\eqn {
n = \min(\{t:size(A_t)< \alpha, T\})
}

Let $Q(k)$ be the expected reward for arm $k$ and $\mu^*$ be the expected reward for the best arm.

\eqn {
R_n = & \max_{i=1...K} E\left[\sum_{t=1}^n Y_{it} - \sum_{t=1}^n Y_{I_t,t} \right] \\
= & E[n]\left(\mu^*  - E[Q]\right) 
}

Without loss of generality, assume the arms are ordered from best to worst.

\eqn{
& Q(k = 1...K) = [\mu^*, \mu^*-d_2 ... \mu^*-d_k] \\
&\implies E[Q] = \mu^* - \frac{1}{K}\sum_{k=2}^K d_k \\
&\implies  R_n = E[n]\left(\frac{1}{K}\sum_{k=2}^K d_k \right)
}

Whenever the following two statements hold only arms with indexes less than $\alpha$ can be in the set $A_t$:

\eqn {
& \mu^* - \hat{\mu}^* \leq \frac{d_\alpha}{2} \\
& \hat{\mu_k} - \mu_k \leq \frac{d_k}{2} \; \forall k \geq \alpha 
}

\eqn{
\label{eq:proboverlap}
\implies \rho(t) \equiv P(\exists k \in A_t: k \geq \alpha)  \leq P(\mu^* - \hat{\mu}^* > \frac{d_\alpha}{2}) + \sum_{k=\alpha}^K P( \hat{\mu_k} - \mu_k > \frac{d_k}{2})
}

\eqn {
P(n > t) = \begin{cases} 0 & \text{if } t \geq T \\
P(\exists k \in A_t: k \geq \alpha) & \text{otherwise}
\end{cases}
}

We now concentrate bounding \ref{eq:proboverlap}. For random variables $W_{sij} = P(Y|X_i=j)$ drawn from a Bernoulli distribution with mean $p_{ij}$ the Chernoff inequality gives:

\eqn {
& P(\frac{1}{t}\sum_s W_{sij} - p_{ij} \geq \gamma) \leq \exp(-\frac{t\gamma^2}{2p_{ij}(1-p_{ij})+2\gamma/3}) \\
\implies & P(\frac{1}{t}\sum_s \frac{W_{sij}}{p} - \frac{p_{ij}}{p} \geq \epsilon) = P(\hat{\mu}_k - \mu_k \geq \epsilon) \leq \exp(-\frac{tp\epsilon^2}{2+2\epsilon/3}) = \exp(-\frac{t\epsilon^2}{4+4\epsilon/3})
}
Where $p_{ij} = P(Y = 1, X_i = j) \leq P(X_i=j) = p = 1/2 \;\;\; \forall(i,j)$

Similarly, 
\eqn {
P(\mu^* - \hat{\mu}^* \geq \epsilon) \leq exp(-tp^2\epsilon^2) = exp(-\frac{t\epsilon^2}{4})
}

\eqn {
\implies \rho(t) \leq \exp(-\frac{ d_\alpha^2 t}{16}) + \sum_{k=\alpha}^K exp(-\frac{d_k^2 t}{16(1+d_k/6)})
}

\eqn{ 
E[n] = & \sum_{t=1}^T P(n \geq t) \leq \sum_{t=1}^T \rho(t) \\
= & \min \left(T, \frac{1 - e^{-d_\alpha^2 T/16}}{e^{d_\alpha^2 /16} -1 } +  \sum_{k=\alpha}^K \frac{1 - e^{-d_k^2 T/16(1+d_k/6)}}{e^{d_k^2 /16(1+d_k/6)} -1 } \right)
}

Since the regret is $R_n = E[n]\left(\frac{1}{K}\sum_{k=2}^K d_k \right)$ the worst case is that just enough of the differences $d_k$ are $0$ to make $E[n] = T$ and the remainder are $1$. This occurs if $d_\alpha = 0$, In this case the regret is:

\eqn {
R_n = T \left(\frac{K-(\alpha+1)}{K}\right)
}

Clearly, this is not quite the right criteria to decide when to switch ...

What about if I

\subsubsection{Regret on observing for h rounds before switching to UCB}

How large the regret is if we initialize with a certain number of counts already in place...

Suppose we have $O_i$ observations for arm $i$. We will now begin doing standard UCB - storing a separate set of bounds, only each time we choose an action we will pick the narrower of the observational/interventional confidence bounds.

\eqn{
\hat{\epsilon}_{it} &= \min \left( \sqrt{\frac{\alpha \log(t)}{2 T_{it}}},\sqrt{\frac{log(1/\delta)}{2 O_i}} \right)\\
\label{eqn:combinedBoundsEpsilon}
& = \sqrt{\frac{\alpha \log(t)}{2 \max(T_{it},O_i)}} \;\; \text{if we let $\delta = t^{-\alpha}$}
}

When running UCB, in order to select a non-optimal arm $i$ at timestep $t$, at least one of the following statements must be true:

\begin{enumerate}
\item $\hat{\mu}_{i^*t} + \hat{\epsilon}_{i^*t} \leq \mu_i + \Delta_i$
\item $\hat{\mu}_{it} + \hat{\epsilon}_{it} \geq \mu_i + 2\hat{\epsilon}_{it}$
\item $\Delta_i < 2 \hat{\epsilon}_{it}$
\end{enumerate}

Given our expression for the confidence bound in equation \ref{eqn:combinedBoundsEpsilon} we can write statement (3) as:
\eqn{
\max(T_{it},O_i) < \frac{2\alpha \log(t)}{\Delta_i^2}
}

Let:

\eqn{
\beta = \frac{2\alpha \log(n)}{\Delta_i^2} 
}

If $O_i \geq \beta$, statement (3) is guaranteed to be false for all $t$ and we can bound the expected number of times we select $i$ with how many times we expect the bounds given by (1) and (2) to be true.

For arms $i$ such that $O_i \geq \beta$

\eqn{
&P(\text{1 is true}) < t^{1-\alpha}\\
&P(\text{2 is true}) < t^{1-\alpha}\\
& \implies P(I_t = i) < 2t^{1-\alpha}\\
& \implies R_n(i) \leq \frac{\Delta_i \alpha}{\alpha -2}
}

For all other arms with $\Delta_i > 0$, the bound is the same as standard UCB
\eqn{
R_n(i) \leq  \frac{2\alpha \log(n)}{\Delta_i} + \frac{\Delta_i \alpha}{\alpha -2} 
}

Assume we observed for $h$ steps. The expected regret from this period is just $h E[\Delta_i]$. Let $T = h+n$ be the total time.

\eqn{
R_T < \sum_{i=1}^K \Delta_i \left(\frac{h}{K} + \frac{\alpha}{\alpha-2}\right) + \sum_{i:\Delta_i > 0}P(O_i \leq \beta)\frac{2\alpha \log(n)}{\Delta_i}
}

Using Hoeffding's Inequality:

\eqn {
P(O_i \leq \beta) \leq \begin{cases}
2 e^{-2h(\frac{1}{2}-\frac{\beta}{h})^2} & \text{if $h > 2\beta$} \\
1 & \text{otherwise}
\end{cases}
}

Its tricky - selecting the $h$ to switch at based on the inequality can certainly yield a non-optimal answer. Maybe I should figure this out via simulation?? But some theory to tell me what to simulate would certainly help.

\pagebreak

\subsubsection{General rough thoughts}

When observing the confidence interval on all the arms drops approximately with $\sqrt{\frac{1}{n}}$ (provided that the probability of each occurring is the same) - otherwise for each arm it will be weighted by this drop will be weighted by a function of the probability that it occurs. When acting, the interval on a single arm we intervene on drops. What is the informational value of reducing the bounds on various arms (it is higher for arms that are more likely to be good).

\subsection{Bounding a weighted sum of unbiased estimators with McDiarmid's Ineqaulity}

McDiarmid's Inequality states:
If $X_i \ci X_j$ and 
\eqn{
|\phi(X_1...X_i...X_N) - \phi(X_1...X_i^{'}...X_N)| < c_i \;\; \forall i
}
\eqn{
& P\left(|\phi(\boldsymbol{X}) - E[\phi(\boldsymbol{X})]| \geq \epsilon \right) \leq 2 \exp \left(-\frac{2 \epsilon^2}{\sum_{i}c_i^2} \right)\\
\label{eqn:McDiarmid}
& P\left(|\phi(\boldsymbol{X}) - E[\phi(\boldsymbol{X})]| \geq 
\sqrt{\frac{\sum_{i}c_i^2}{2}\log{\frac{2}{\delta}}} 
\right) \leq \delta
}

In our problem, for each variable $V_i$ and value $j$ we have:

\eqn{
\hat{\mu}_a = \tilde{P}(Y|V_i = j)= \begin{cases}
\frac{p_a}{n_{a1}}\sum_{s=1}^{n_{a1}}X_{a1,s} + \frac{1-p_a}{n_{a0}}\sum_{s=1}^{n_{a0}}X_{a0,s} & \text{ if $a \neq i$}\\
\sum_{s=1}^{n_i}X_s & \text{if $a = i$}
\end{cases}
}

where $X_{a1,s}  \sim P(Y|V_i = j, do(V_a = 1))$ and $X_{a0,s}  \sim P(Y|V_i = j, do(V_a = 0))$, both $\in [0,1]$. We then pool $\{\hat{\mu}_1 ... \hat{\mu}_K \}$ to get a single estimate.

\eqn {
\hat{\mu} = \tilde{P}(Y|V_i = j)= \sum_a w_a \hat{\mu}_a \text{, where } \sum_a w_a = 1
}

Let

\eqn {
\hat{\mu} = \phi(\boldsymbol{X}) = \sum_{a \neq i} w_a \left[ 
\frac{p_a}{n_{a1}}\sum_{s=1}^{n_{a1}}X_{a1,s} + \frac{1-p_a}{n_{a0}}\sum_{s=1}^{n_{a0}}X_{a0,s}
\right] + \frac{w_i}{n_i} \sum_{s=1}^{n_i}X_{i,s}
}

Note: this treats the number of samples $n_i$,$n_{a1}$, and $n_{a0}$ as fixed. Even for fixed actions, the latter two are still random variables that depend on $\boldsymbol{p}$  Will this bound still hold?

\eqn {
&\phi(...X_{\alpha 1,s}...) - \phi(...X_{\alpha 1,s}^{'}...) \leq w_\alpha \frac{p_\alpha}{n_{\alpha 1}} \\
&\phi(...X_{\alpha 0,s}...) - \phi(...X_{\alpha 0,s}^{'}...) \leq w_\alpha \frac{1-p_\alpha}{n_{\alpha 0}}\\
& \phi(...X_i...) - \phi(...X_i^{'}...) \leq \frac{w_i}{n_i}
}

\eqn{
\sum_i c_i^2 = & n_i \left(\frac{w_i}{n_i}\right)^2+ \sum_a \left[ n_{a1}\left(w_a \frac{p_a}{n_{a1}}\right)^2 + n_{a0}\left(w_a \frac{1-p_a}{n_{a0}}\right)^2\right]\\
= & \frac{w_i^2}{n_i}+ \sum_a w_a^2 \left(\frac{p_a^2}{n_{a1}}+  \frac{(1-p_a)^2}{n_{a0}} \right) \\
\label{eq:tominimize}
= & \sum_a w_a^2 f(a) \text{, where }\\ 
f(a) =& \begin{cases}
\frac{p_a^2}{n_{a1}}+  \frac{(1-p_a)^2}{n_{a0}}  & a \neq i\\
\frac{1}{n_i} & a = i
\end{cases}
}

We want to choose weights $\boldsymbol{w}$ so as to minimize \ref{eq:tominimize} subject to the constraint $\sum_a w_a = 1$.

The minimum (assuming it exists) should occur at a critical point of:

\eqn {
L(w_1...w_k,\lambda) = \sum_a w_a^2 f(a) + \lambda((\sum_a w_a)-1)
}

\eqn{
& \frac{\partial L}{\partial w_a}  = 2 w_a f(a) + \lambda = 0 \\
& \implies w_a =  \frac{-\lambda}{2 f(a)}\\
& \frac{\partial L}{\partial \lambda}  = (\sum_a w_a)-1= 0 \\
& \implies -\frac{\lambda}{2}\sum_a \frac{1}{f(a)} = 1
 \implies \lambda = -\frac{2}{\sum_a \frac{1}{f(a)}}\\
& \implies w_a = \frac{1}{f(a)\sum_a \frac{1}{f(a)}} \\
\label{eqn:sumofsquares}
& \implies \sum_i c_i^2 = \frac{1}{\sum_a \frac{1}{f(a)}} 
}

Substituting \ref{eqn:sumofsquares} into the McDiarmid inequality \ref{eqn:McDiarmid}:

\eqn{
P\left(|\hat{\mu}^{ij} - \mu^{ij}| > \sqrt{\frac{1}{2\sum_a \eta_a^{ij}} \log{\frac{2}{\delta}}}\right) \leq \delta
}

where:

\eqn {
& \mu^{ij} = P(Y | V_i = j) \\
& \eta_a^{ij} = \begin{cases}
\frac{n_{a1}^{ij} n_{a0}^{ij}}{n_{a1}^{ij}(1-p_a)^2+n_{a0}^{ij}p_a^2} & a \neq i\\
n_{ij} & a = i
\end{cases} \\
&n_{al}^{ij} = \sum_{s=1}^t \ind{do(V_a = l), V_i = j} \\
& n_{ij} = \sum_{s=1}^t \ind{(do(V_i = j)}
}

All of the above is to get estimates for $P(Y|V_i = j)$ for some fixed $i,j$. Suppose we explore for some fixed total number of rounds $h$, the goal is to minimize the worst confidence bound - that doesn't quite make sense as a goal - we just need to be sure that all actions are worse than our estimate of the best with probability $\delta$. ... anyway

We have control of are the number of times we do each action, $n_{al}$, which obviously also influences the random variables $n_{al}^{ij}$, subject to the constraint $\sum n_{al} = h$.

Objective: minimize the expectation of the largest confidence bound after a fixed number of rounds $n$.

Let $\boldsymbol{n} = [n_{11},n_{10},n_{21},n_{20}...n_{k1},n_{k0}]$

\eqn{
\tilde{\boldsymbol{n}} = \argmin_{\{\boldsymbol{n}:\|\boldsymbol{n}\|=h\}} \max_{i,j} \left( E \left[ \sqrt{\frac{1}{2\sum_a \eta_a^{ij}} \log{\frac{2}{\delta}}} \right] \right)
}

We can bound the first part of $\eta_a^{ij}$

\eqn {
\eta_a^{ij} = \frac{n_{a1}^{ij}n_{a0}^{ij}}{n_{a1}^{ij}(1-p_a)^2+n_{a0}^{ij}p_a^2} & \leq \frac{n_{a1}^{ij}n_{a0}^{ij}}{\max(n_{a1}^{ij}(1-p_a)^2+n_{a0}^{ij}p_a^2)} \\
& = \min \left( \frac{n_{a0}^{ij}}{(1-p_a)^2}, \frac{n_{a1}^{ij}}{p_a^2} \right)
}

\eqn {
E \left[ \min \left( \frac{n_{a0}^{ij}}{(1-p_a)^2}, \frac{n_{a1}^{ij}}{p_a^2} \right)  \right] & \leq 
\min \left( E\left[\frac{n_{a0}^{ij}}{(1-p_a)^2} \right], E\left[\frac{n_{a1}^{ij}}{p_a^2} \right] \right) \\
& = P(V_i = j) *\min \left( \frac{n_{a0}}{(1-p_a)^2} , \frac{n_{a1}}{p_a^2}  \right) \\
}

\begin{figure}[H]
\centering
\caption{The effective number of samples $\eta_a$ versus $n_{a1}$, where $p_a = .8$ and the total number of samples,  $ n_{a1}+n_{a0}=100$. The effective number of samples is maximized (and equals the total) if we sample each side according to its probability.}
\includegraphics[width=.5\textwidth]{samplehalves}
\end{figure}

\subsection{Targeted Sampling}
Sample a equal number of points from each arm - until the error on all arms is smaller than some threshold. Then exploit. This should do better than observe-exploit, particularly where the probability of some events occurring without intervention is low.

A more sophisticated version:

\subsection{UCB variant}
Combine estimators according to:

\eq {
w_a     &= \frac{n_a}{\sum_{a=1}^K n_a} \text{ and } n_{i,j}=\begin{cases} 
n_{i,j} & \text{if } a = i \\
\frac{1}{2}\min\set{\frac{n_{a,1}}{p_a}, \frac{n_{a,0}}{1-p_a}}  & \text{otherwise}
\end{cases}
}

In this case the estimators from section \ref{sec:estimators} are biased - so its a lot harder to prove a regret bound.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{times}
\usepackage{fullpage}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{accents}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{dsfont}
\usepackage[bf]{caption}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={My title},    % title
    pdfauthor={Author},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\usepackage{amsthm}
\usepackage{natbib}
\usepackage[capitalize]{cleveref}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{tikz} 
\usetikzlibrary{arrows,positioning} 
\pgfarrowsdeclarecombine{ring}{ring}{}{}{o}{o}
%\DeclareMathOperator{\ringarrow}{\raisebox{0.5ex}{\tikz[baseline]{\draw[ring->](0,0)--(2em,0);}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MACROS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\defined}{\vcentcolon =}
\newcommand{\rdefined}{=\vcentcolon}
\newcommand{\E}[1]{\mathbb E\left[#1\right]}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\calF}{\mathcal F}
\newcommand{\sr}[1]{\stackrel{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\ind}[1]{\mathds{1}\!\!\set{#1}}
\newcommand{\argmax}{\operatornamewithlimits{arg\,max}}
\newcommand{\argmin}{\operatornamewithlimits{arg\,min}}
\newcommand{\floor}[1]{\left \lfloor {#1} \right\rfloor}
\newcommand{\ceil}[1]{\left \lceil {#1} \right\rceil}
\newcommand{\eqn}[1]{\begin{align}#1\end{align}}
\newcommand{\eq}[1]{\begin{align*}#1\end{align*}}
\newcommand{\Ber}{\operatorname{Bernoulli}}
\renewcommand{\P}[1]{\operatorname{P}\left\{#1\right\}}
\newcommand{\N}[2]{\mathcal{N}\left({#1}\;,\;{#2}\right)}

\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    observed/.style={
           circle,
           rounded corners,
           draw=black, thick,
           minimum width=2.5em,
           minimum height=2.5em,
           font=\footnotesize,
           text centered,
           scale=1,
           fill=blue!20!white},
     latent/.style={
           circle,
           rounded corners,
           draw=black, thick, dashed,
           minimum width=2.5em,
           minimum height=2.5em,
           font=\footnotesize,
           text centered,
           fill=black!10!white
           },
     empty/.style={
           circle,
           rounded corners,
           minimum width=.5em,
           minimum height=.5em,
           font=\footnotesize,
           text centered,
           },
    % Define arrow style
    pil/.style={
           o->,
           thick,
           shorten <=2pt,
           shorten >=2pt,},
    sh/.style={ shade, shading=axis, left color=red, right color=green,
    shading angle=45 }  
}

@@

\title{Partial Identifiability}

\begin{document}
\def\ci{\perp\!\!\!\perp}

\subsection*{Adjustment}

\begin{figure}[H]
	\centering    
          \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed}, hidden/.style={empty},background rectangle/.style={fill=olive!45}]
 %nodes
\node[main node](2){$X$};
\node[main node, above right=of 2](3){$Z$};
\node[main node, below right=of 3](4){$Y$};
\node[latent, above=of 2](5){$\varepsilon_x$};
\node[latent, above=of 4](6){$\varepsilon_y$};
 \path[every node/.style={font=\tiny}]
    (3) edge (2) edge (4)
    (2) edge (4)
    (5) edge (2)
    (6) edge (4);
\end{tikzpicture}
\end{figure}

To estimate the causal effect of $X$ on $Y$, we need to condition on $Z$ so as to block the backdoor path $X \leftarrow Z \rightarrow Y$.

\eq {
P(Y|do(X=x)) = \sum_{z \in \mathcal{Z}}P(Y|X=x,Z=z)P(Z)
}

With a binary treatment $X$ we can also write:

\eq{
ATE = E(Y|do(X=1)) - E(Y|do(X=0))
}

This assmumes $Z$ is fully observable, ie there are no unobservable variables, $U$ that cause both $X$ and $Y$.

\subsection*{Covariate Shift}

Seperate from the problem of adjustment, lets define covariate shift.

\begin{itemize}
\item We have training data $d_{train} = \set{(x_1,y_1),...,(x_n,y_n)}$ sampled from $P(X,Y) = P(X)P(Y|X)$.
\item The test data $d_{test} = \set{(x'_1,y'_1),...,(x'_{n'},y'_{n'})}$ is assumed to be sampled from $Q(X)P(Y|X)$, where $Q(X) \neq P(X)$. As usual for test data, we observe only the inputs $\set{x'_1,...,x'_{n'}}$
\item We wish to use the training data to learn a hypothosis/function $h:\mathcal{X} \rightarrow \mathcal{Y}$ that minimises $\sum_{i = 1}^{n'}\mathcal{L}(h(x'_i,y'_i))$, where $\mathcal{L}$ is some loss.
\end{itemize}

The covariate shift assumption is that $P(Y|X)$ has not changed.

%This assumption is plausible if $X$ causes $Y$ and we imagine a mechanism that maps $\mathcal{X}$ to $\mathcal{Y}$ that is independent of the input distribution. If $Y$ causes $X$ then we would expect that $P(X)$ and $P(Y|X)$ would in general be related, such that a shift in $P(X)$ would lead us to ancipate that $P(Y|X)$ might also have changed.

Although we have assumed the underlying mapping, $P(Y|X)$, we are trying to learn has not changed between the test and the train data we still need to adapt standard prediction algorithms as otherwise (through a preference for 'simple' functions) we may select a function that fits well where $P(X)$ is high but performs badly where $Q(X)$ is high. There are some situations that require no adaptation. For example, if the true function is linear and we fit an (unregularized) linear model, then model that is in expectation optimal on the training data is also optimal for the test data. Another interesting example is if the model is a Gaussian process \cite{}.

\subsection*{Covariate shift in the adjustment problem}

In the adjustment problem, we have observational training data, $d_{train} = \set{(x_1,z_1,y_1),...(x_n,z_n,y_n)} \sim P(Z,X)P(Y|Z,X)$. If we intervene and set $X=x$ then the data will be sampled from $P(Z)\delta(X-x)P(Y|Z,X)$. Note that the covariate shift assumption is satisfied in this scenario, $P(Y|Z,X)$ does not change between the train and test settings. What has changed is the joint distribtion $P(X,Z)$.
